Figures

### 2019-05-17 figures/10_nitrogen_deposition.Rmd
add some autocorellation todos

```{r 08_exploratory_dotplot, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dt %>% 
  dplyr::select(tp, tn, lake_area_ha:wheat, 
                matches("cultivated_crops")) %>%
  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  dplyr::select(-mixed.crop, -matches("other"), -forage, 
                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

plot(lg$hu12.chag$hu12_dep_totaln_2010_mean, 
     lg$hu12.chag$hu12_prism_ppt_30yr_normal_800mm2_annual_mean)

ggplot(data = dt_sub) + 
  geom_point(aes(x = ))

@@

ggplot(data = prep_dotplot(dt_ndep, "nitrogen_atmospheric_deposition")) +
    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var)) +
    plot_opts

>>>>

```{r 10_nitrogen_deposition, echo=FALSE, message=TRUE, eval=TRUE}
dt     <- readRDS("../data/dt.rds")
dt_sub <- dt %>% 
  dplyr::select(tp, tn, lake_area_ha:wheat, 
                matches("cultivated_crops")) %>%
  dplyr::select(-row_crop_pct, -ag_pct, -pasture_pct) %>% # rm nlcd
  dplyr::select(-mixed.crop, -matches("other"), -forage, 
                -hu12_ppt_std, -water, -developed, -forest) %>% # rm junk
  dplyr::filter(complete.cases(.)) %>%
  mutate_all(as.numeric) %>%
  data.frame(stringsAsFactors = FALSE)

@@

ggplot(data = prep_dotplot(dt_ndep, "nitrogen_atmospheric_deposition")) +
    geom_point(aes(x = nitrogen_atmospheric_deposition, y = var))

# ---- scatterplots ----
# plot n_dep vs ppt
# plot n_dep vs baseflow

# plot(lg$hu12.chag$hu12_dep_totaln_2010_mean, 
#      lg$hu12.chag$hu12_prism_ppt_30yr_normal_800mm2_annual_mean)

# ggplot(data = dt_sub) + 
#   geom_point(aes(x = ))

# ---- autocorrelation_plots ----
# spind::acfft()
